---
title: "Using the HeelLife Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the HeelLife Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `HeelLife` package provides a single, powerful function, `get_unc_contacts()`, to automate the process of scraping student organization contact data from the UNC Chapel Hill 'Heel Life' website. This vignette will walk you through the necessary setup and usage.

## Prerequisites

Before using the package, you must have **Mozilla Firefox** installed on your computer. The package's scraping engine relies on the `RSelenium` package, which will programmatically control a Firefox browser to perform the scraping task.

## Installation

First, install the `HeelLife` package. If it's on CRAN, you can run:
```r
install.packages("HeelLife")
```
Alternatively, you can install the development version from GitHub:
```r
# install.packages("devtools")
devtools::install_github("YOUR-USERNAME/HeelLife")
```

## Storing Credentials Securely

The `get_unc_contacts()` function requires your UNC ONYEN and password. To avoid writing them directly in your script, we strongly recommend using environment variables. The `dotenv` package is excellent for this.

1.  Create a file named `.env` in your project's root directory.
2.  Add your credentials to this file:
    ```
    ONYEN_USERNAME="your_onyen"
    ONYEN_PASSWORD="your_password"
    ```
3.  Ensure this `.env` file is listed in your `.gitignore` file to prevent it from being committed to version control.

## Running the Scraper

With your credentials stored, you can now run the scraper.

```{r, eval=FALSE}
library(HeelLife)
library(dotenv)

# Load credentials from the .env file
load_dot_env()

my_username <- Sys.getenv("ONYEN_USERNAME")
my_password <- Sys.getenv("ONYEN_PASSWORD")

# Check if credentials were loaded
if (!nzchar(my_username) || !nzchar(my_password)) {
  stop("Please set ONYEN_USERNAME and ONYEN_PASSWORD in a .env file.")
}

# Execute the scraping function
# This will open a Firefox window and prompt you for MFA in the R console.
contacts_df <- get_unc_contacts(
  username = my_username,
  password = my_password,
  output_file = "heellife_data.csv"
)

# The function returns a data frame and saves it to a CSV.
# You can now work with the data in R.
head(contacts_df)
```

## The Output

The function returns a `tibble` (a modern data frame) with the following columns:

* **Organization**: The name of the student organization.
* **Position**: The title of the contact person (e.g., "President", "Treasurer").
* **Name**: The name of the contact person.
* **Email**: The email address of the contact person.

This data is also saved to the CSV file specified in the `output_file` argument for later use.
